### 2020-01-28 2020/WCGO_MCO_OptimizationLetters/2020_WCGO_MCO.tex
delete reference [18]

The general computational scheme of the \textit{global search algorithm} for multiextremal optimization problems with non-convex constraints \footnote{This method is also known as the index method -- see \cite{c18}.} (AGCS) is as follows \cite{c18}.

>>>>

The general computational scheme of the \textit{global search algorithm} for multiextremal optimization problems with non-convex constraints \footnote{This method is also known as the index method.} (AGCS) is as follows \cite{c18}.
